Forecasting US Presidential Election Results Using Bayesian Prediction

### 2024-10-22 paper/paper.qmd
Update paper.qmd

poll <- read.csv("president_polls.csv")
poll_of_polls <- poll %>%
  group_by(pollster, answer) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  group_by(pollster) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  select(pollster, answer, percentage)
```

>>>>

poll <- read.csv("raw_data.csv")
poll_of_polls <- poll %>%
  group_by(pollster, answer) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  group_by(pollster) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  select(pollster, answer, percentage)
```
